\begin{abstract}
Blockchain technology provides a decentralized and immutable ledger, but its inherent transparency poses a significant barrier to enterprise adoption in domains requiring data privacy. 
  Existing solutions like channels provide data isolation but are coarse-grained, requiring a separate ledger and consensus instance per channel. In this paper, we introduce
  \textit{private data collections}, a mechanism for managing private data on permissioned blockchains. Our approach decouples private data storage from the replicated ledger:
  private data is shared only among authorized peers, while cryptographic hashes are recorded on the ledger for tamper-evidence and serializability verification. The key 
  theoretical contribution is \textbf{blind validation}: we prove that on-chain hashes form a \textit{conflict-complete proxy} for private state---OCC-based serializability
  checks on hashed state detect exactly the same conflicts as checks on the underlying private data, producing neither false negatives nor false positives. This enables the
  entire network to verify the correctness and serializability of private transactions without ever accessing the private data itself. We design a two-phase gossip-based protocol
  for proactive dissemination and reactive retrieval of private data, and we formalize the collection abstraction with seven design requirements. Our solution is designed for any
  blockchain platform that follows the simulate-order-validate-commit replication protocol. We implement it in Hyperledger Fabric and demonstrate that private data collections add
  only 3--14\% overhead to transaction throughput while providing fine-grained data privacy. The mechanism has been in production since Hyperledger Fabric v1.2 and is deployed by
  organizations including Walmart, MediLedger, Honeywell, Oracle and GSBN.
\end{abstract}
