\section{Background and Motivation}
some text \ldots

\subsection{Architecture of Hyperledger Fabric}
some text \ldots

\par
\textbf{(1) Endorsement Phase.} some text \ldots

\par
\textbf{(2) Ordering Phase.} some text \ldots

\par
\textbf{(3) Validation Phase.} some text \ldots

\par
\textbf{(4) Commit Phase.} some text \ldots

\subsection{Motivation for Data Privacy}
\par
some text \ldots
\subsubsection{Use Case Study: Food Traceability}
In September 2006, there was an outbreak of food-borne illness caused by Escherichia coli~\cite{ecoil}
bacteria in 26 U.S. states. This outbreak was linked to bagged spinach. By October 6, 2006, 199 people had been
infected, including three people who died and 31 who suffered kidney failure. It took regulators two
weeks to conduct the backtrace and determine the exact source of the outbreak. During those two weeks,
many people got sick and tons of good spinach was unnecessarily discarded---wrongfully
wasted because we could not tell the good spinach from the bad~\cite{blockchain-for-business}.
An efficient food traceability mechanism is the key to reduce the backtrace time in such a scenario.
Traceability is the ability to track and record the movement of food products throughout a supply chain, which
includes growing, harvesting, packing, manufacturing, repacking, storage, distribution, and sale to the consumer.
With these information, it is possible to trace backward in the supply chain (usually to find the source of a
problem) as well as trace forward (usually to do a recall of contaminated products).
\par
Food Standards Australia New Zealand (FSANZ)~\cite{}, European Commission's food safety policy~\cite{}, and Food and Agriculture
Organization of United Nations (FAO)~\cite{} provide various guidelines~\cite{} on what records need be kept in order to enable
food traceability. The following are some of the records:
\begin{enumerate}[topsep=0pt,noitemsep,leftmargin=15pt]
	\item name and address (and other contact details) of suppliers/farmers and a description of products or inputs supplied.
	\item the name and contact information of the transporter and a description of products transpoted.
	\item name and addresses (and other contact details) of customers and a description of the product supplied to them.
    \item date of transaction or delivery.
    \item batch or lot identification (or other markings such as product ID).
    \item volume or quantity of product supplied or received.
	\item raw materials used.
	\item conservation and storage methods for the product.
\end{enumerate}
As a result, when an outbreak of food-borne illness occurrs, it would be possible to traceback from the customer
to product ID to the supplier/farmer. Similarly, a recall can be performed by tracing forward from the supplier/farmer
to product lot to customers. If these records are kept in the form of papers or in a centralized database, during
an outbreak, a lot of communication needs to happen between various food business operators to perform traceback
or traceforward. Such a method is very inefficient, time consuming, and expensive. Hence, a blockchain based food traceability
solution is needed for food safety, to improve efficiency, to allow us to easily communicate information that customers
are asking for (i.e., fork to farm), and to help autheticate claims made in a product. With blockchain, network members
can track the food products as they travel from farm to fork. Recently, Walmart did an experiment that traced
the origin of sliced mangos from Walmart stores back to the farm. This process showed a radical improvement from
approximately seven days it took to conduct the backtrace by using traditional methods down to 2.2
seconds~\cite{7-to-2, walmart-hf} using Hyperledger Fabric.
\par
As blockchain is a replicated ledger, storing all information related to a food supply chain could leak
proprietary or business competitive information. For example, invoice details cannot be shared as it could leak
the business contract between the farmer and the distributor or the distributor and the transporter. As customer
contact details are very sensitive, it is not advisable to store it in the replicated ledger. Figure~\ref{} shows
the actors involved in a food traceability blockchain network along with different interaction between them.
\\
TODO: \\
(1) Add a figure. \\
(2) Explain the transaction flow between various actors. \\
(3) What data are sensitive within a transaction. \\
\subsubsection{Existing Solutions and Drawbacks}
some text \ldots
\par
\textbf{(1) Fabric Channel.}
some text \ldots
\par
\textbf{(2) Quorum~\cite{} Private Transaction.}
some text \ldots
\par
\textbf{(3) Encryption of Data.}
some text \ldots
\par
\textbf{(4) Off-chain Storage With an On-chain Proof.}
some text \ldots
\par
\textbf{(5) Zero Knowledge Proof.}
some text \ldots
