\section{Design of Private Data Transaction Processing}
\label{s:design}
To achieve data privacy while maintaining the integrity and consistency of the blockchain, we propose an integrated architecture based on the \textit{execute-order-validate-commit} paradigm. Our design employs a \textit{dual-layered storage strategy} and \textit{partitioned state management} to isolate private data while ensuring global verifiability. Figure~\ref{fig:pdc-flow} provides an end-to-end overview of the private data collection transaction flow, with numbered steps spanning all four phases. The subsequent subsections detail each phase.

\subsection{Transaction Simulation}
\input{sections/apis.tex}
The simulation phase (steps 1--4 in Figure~\ref{fig:pdc-flow}) begins when a client submits a transaction proposal to a subset of peers that are members of the relevant collections, satisfying \textbf{R4} (Authorized Execution Only) by ensuring that private data is only processed on authorized nodes. The client provides private data through a \emph{transient data} field in the proposal. This transient data is used by the smart contract during execution but is excluded from the final transaction payload, preventing private data from being broadcast to the entire network during ordering.

Upon receiving the proposal, each endorsing peer executes the smart contract, which interacts with public and private state through the APIs defined in Table~\ref{table:apis}. Public data operations (\texttt{GetState}, \texttt{PutState}, \texttt{DelState}) access the standard replicated state, while private data operations (\texttt{GetPrivateData}, \texttt{PutPrivateData}, \texttt{DelPrivateData}) access collection-specific private state. A single transaction may read and write both public and private state within the same smart-contract invocation; however, doing so requires that the endorsing peers satisfy both the smart contract's endorsement policy (for public writes) and the collection's endorsement policy $\mathcal{E}$ (for private writes). In practice, this means the two policies must be the same or overlapping. When the policies do not overlap, a transaction may still read from public state while reading and writing private state, since reads do not require endorsement. Crucially, each private data write API performs dual-recording: for example, \texttt{PutPrivateData}$(c, k, v)$ writes $(k, v)$ to the private write-set for collection $c$ and simultaneously records $(H(k), H(v))$ in the hashed write-set, satisfying \textbf{R2} (Hash-Data Integrity) by ensuring that every update to private state is inextricably linked to the verifiable public ledger.

On successful execution, the peer constructs three types of read-write sets: (1) a \textit{public read-write set} capturing reads and writes to the replicated ledger state, (2) a \textit{hashed read-write set} containing only cryptographic hashes of private keys and values, and (3) one or more \textit{private write-sets}, one per collection involved in the transaction. The example in Table~\ref{table:apis} illustrates how a sequence of API calls produces these partitioned outputs. The endorsing peer signs the public and hashed read-write sets as part of its endorsement response and returns it to the client, while the private write-sets are stored in the peer's transient store and proactively disseminated to other collection members as described in \S\ref{s:gossip}.

Because the final order of transactions is determined after simulation, there is a critical temporal gap during which a private write-set may become orphaned if its transaction is later invalidated. Directly writing private data to the permanent store would violate the isolation guarantee, as invalid transactions could corrupt committed state. To address this, nodes utilize a transient store to persist private write-sets, isolating uncommitted private state from the permanent ledger, which is essential for \textbf{R1} (Transactional Atomicity and Isolation). Since multiple transactions may be simulated concurrently, the transient store uses the transaction identifier ($txid$) as the primary key to prevent collisions. Data remains in the transient store until the transaction is successfully ordered and reaches the commit phase.

\subsection{Partitioned State Management}
A key challenge in this architecture is integrating private data into the ledger without violating the ``blind'' validation requirement. We solve this by partitioning the state database into three logical domains. Each smart contract is allocated a dedicated \textit{namespace} within these domains, and the access and modification of data within a namespace are governed by an endorsement policy specifying the set of authorized nodes whose signatures are required to validate state changes. The three logical spaces for each namespace are:
\begin{itemize}[topsep=0pt,noitemsep,leftmargin=15pt]
    \item \textit{Public State:} Accessible to all nodes; contains the standard replicated ledger state.
    \item \textit{Hashed State:} Replicated across all nodes; contains cryptographic hashes of private keys and values, providing the evidence required for tamper-detection and serializability checks.
    \item \textit{Private State:} Isolated to authorized nodes; contains the actual private key-value pairs. Modifications are governed by the collection's own endorsement policy $\mathcal{E}$, which supersedes the smart contract's default endorsement policy for private data operations.
\end{itemize}
A key consequence of this partitioning is that Public State and Hashed State are consistent across all peers in the network, providing a globally uniform view of the ledger. Private State, however, varies from peer to peer depending on which collections each peer's organization is a member of---a peer only maintains private state for collections in which it is authorized. This partitioning satisfies \textbf{R3} (Smart-Contract Controlled Access) by confining all private data interactions to smart-contract namespaces, and reinforces \textbf{R2} (Hash-Data Integrity) by maintaining a replicated Hashed State that mirrors the private state's structure.

\subsection{Transaction Validation and Commit}
The validation (step 8) and commit (steps 9--10) phases in Figure~\ref{fig:pdc-flow} ensure that only correctly endorsed and serializable transactions are permanently recorded. Before a transaction is committed, nodes verify that it has been endorsed according to the smart contract's endorsement policy for public state changes and the collection's endorsement policy $\mathcal{E}$ for private state changes, satisfying \textbf{R4} (Authorized Execution Only) and preventing unauthorized entities from recording fraudulent data or hashes on the public ledger. The system then performs OCC checks using both the public read-write set and the hashed read-write set: for public state, the validator compares the read versions in the transaction against the current Public State; for private state, the validator compares the hash versions in the transaction against the current Hashed State. A critical property of this design is that the Hashed State serves as a perfect proxy for the Private State for version tracking. Since every update to a private key $k$ is accompanied by a mandatory update to its hash $H(k)$ in the public ledger, the version identifiers in the Hashed State are sufficient to detect all write-write and read-write conflicts on private data. This ``blind validation'' allows the entire network to verify the serializability of both public and private state changes without ever seeing the private data itself.

We now formalize the correctness of blind validation. We adopt the standard OCC serializability criterion~\cite{occ}: a transaction $T_i$ is \textit{serializable} with respect to a committed history if no key in $T_i$'s read-set has been modified by any transaction $T_j$ that committed after $T_i$ began execution (i.e., the read-set versions at simulation time match the current committed versions at validation time). Let $\mathcal{S}_P$ denote the Private State and $\mathcal{S}_H$ denote the Hashed State. Let $\text{ver}(s, k)$ denote the version of key $k$ in state $s$.

\smallskip
\noindent\textbf{Theorem 1} (Conflict-Complete Proxy). \textit{The Hashed State $\mathcal{S}_H$ is a conflict-complete proxy for the Private State $\mathcal{S}_P$: for any transaction $T_i$ involving private data, an OCC conflict exists in $\mathcal{S}_P$ if and only if a corresponding conflict exists in $\mathcal{S}_H$. Formally, for every private key $k$ in collection $c$:}
$$\text{ver}(\mathcal{S}_P, k) \neq \text{ver}_{\text{sim}}(T_i, k) \iff \text{ver}(\mathcal{S}_H, H(k)) \neq \text{ver}_{\text{sim}}(T_i, H(k))$$

\textit{Proof.} We establish three invariants maintained by the API (Table~\ref{table:apis}):
\begin{enumerate}[topsep=0pt,noitemsep,leftmargin=15pt]
    \item \textit{Write Bijection:} By construction, every \texttt{PutPrivateData}$(c, k, v)$ atomically produces both a private write-set entry $(k, v)$ and a hashed write-set entry $(H(k), H(v))$. The commit procedure assigns both entries the same version identifier (block number, transaction index). \texttt{DelPrivateData} and \texttt{PurgePrivateData} similarly produce corresponding hashed entries. Thus, $\text{ver}(\mathcal{S}_P, k)$ and $\text{ver}(\mathcal{S}_H, H(k))$ are updated in lockstep: $\text{ver}(\mathcal{S}_P, k) = \text{ver}(\mathcal{S}_H, H(k))$ after every committed transaction.
    \item \textit{Read Recording:} Every \texttt{GetPrivateData}$(c, k)$ records $\text{ver}(\mathcal{S}_H, H(k))$ in the hashed read-set. Since Invariant~1 guarantees $\text{ver}(\mathcal{S}_P, k) = \text{ver}(\mathcal{S}_H, H(k))$, this recorded version is identical to the version that would appear in a hypothetical private read-set.
    \item \textit{Conflict Detection:} During OCC validation, a conflict on private key $k$ exists iff $\text{ver}(\mathcal{S}_P, k)$ has changed since simulation. By Invariant~1, $\text{ver}(\mathcal{S}_P, k)$ changes iff $\text{ver}(\mathcal{S}_H, H(k))$ changes. By Invariant~2, the validator compares $\text{ver}(\mathcal{S}_H, H(k))$ against the same baseline. Therefore, the OCC check on $\mathcal{S}_H$ detects a conflict iff the corresponding check on $\mathcal{S}_P$ would.
\end{enumerate}
Since both directions hold, blind validation produces neither false negatives (missed conflicts) nor false positives (spurious invalidations). \hfill $\square$

\smallskip
\noindent\textit{Edge Case: Concurrent Membership Changes.}
A collection's membership policy $\mathcal{M}$ may be updated in the same block that contains private data transactions for that collection. By design, the validator processes transactions within a block sequentially in their committed order: a membership change at transaction index $j$ takes effect for all subsequent transactions $j' > j$ in the same block. This sequential-within-block processing is a deliberate design choice---it avoids the complexity of batch-level policy resolution and ensures deterministic validation across all peers. The result is that the endorsement policy and membership checks applied during validation always reflect the correct policy version. A newly added member will not yet have historical private data at validation time; the reactive retrieval and reconciliation mechanisms (\S\ref{s:gossip}) handle this asynchronously without affecting the validity of the current block's transactions.

Together, Theorem~1 and the sequential policy application ensure \textbf{R1} (Transactional Atomicity and Isolation) across both public and private state.

Once a transaction is successfully validated, the private write-sets are moved from the transient store to the permanent private data store.

\smallskip
\noindent\textit{Handling Missing Private Data.}
A peer may not possess all private write-sets at commit time. During commit, each peer classifies missing private data into two categories: (1)~\textit{eligible missing data}---private data for collections in which the peer's organization is a member but the data has not yet been received (e.g., due to network delays during dissemination), and (2)~\textit{ineligible missing data}---private data for collections in which the peer's organization is not currently a member. The peer records both categories along with the block number and transaction index. Eligible missing entries are fetched via the reactive retrieval protocol described in \S\ref{s:gossip}, satisfying \textbf{R7} (Data Availability). Ineligible entries are retained so that if the organization later becomes a member of the collection, it can identify and synchronize historical private data that it is now authorized to access, supporting \textbf{R5} (Dynamic Membership).

\smallskip
\noindent\textit{Data Lifecycle Management.}
The private data store supports data lifecycle management through a block-indexed retention policy, satisfying \textbf{R6} (Data Lifecycle Management). To comply with privacy regulations like the ``Right to Forget,'' a background process periodically purges expired private data while maintaining the on-chain hashes to ensure the historical audit trail remains tamper-evident.\footnote{While on-chain hashes that remain after purging could, under certain legal interpretations of regulations such as GDPR, still be considered references to personal data, the hash is a one-way function and the remaining hash alone does not reveal any private content. Organizations should seek legal counsel on the applicability of specific data protection regulations to their deployment.}

The design described in this section assumes that private write-sets are available on authorized nodes when needed for commit. In the next section, we address the critical question of \textit{how} this data is disseminated across the network and how missing data is recovered, which is essential for \textbf{R5} (Dynamic Membership) and \textbf{R7} (Data Availability).
