As described in Algorithm~\ref{alg:dissemination}, after simulation the endorsing peer immediately pushes each private write-set to a subset of authorized collection members. Crucially, the endorser does \textit{not} return its signed response to the client until at least $n_{required}$ peers have acknowledged receipt. Blocking on these acknowledgments guarantees that the data exists on multiple peers before the client can submit the transaction for ordering. After sending the endorsement response, a background gossip task continues pushing the write-set to the remaining peers up to $n_{dissem}$ total, spreading coverage without adding to client-observed latency.

We separate $n_{required}$ from $n_{dissem}$ so that operators can tune the two concerns independently. Setting $n_{dissem}$ aggressively ensures most collection members receive the data proactively, which minimizes commit-time reactive pulls; keeping $n_{required}$ small protects endorsement latency.

When the endorser cannot obtain $n_{required}$ acknowledgments before the timeout, it returns a failure to the client, who may retry with different endorsers. We deliberately do not retry dissemination at the endorser: keeping the endorsement critical path simple avoids unbounded retry delays and pushes fault handling to the client, where it belongs.

\begin{algorithm}[h]
\centering
\small
\begin{tabular}{|p{0.92\columnwidth}|}
\hline
\textbf{Proactive Dissemination Protocol} \\
\hline
\textbf{Input:} Transaction $tx$ with private write-sets \\[3pt]
\textbf{At Endorsing Node} $e$ (after simulation): \\
\quad 1. Store all private write-sets for $tx$ in local transient store \\
\quad 2. \textbf{for each} collection $c$ in $tx$'s private write-sets \textbf{do} \\
\quad\quad\quad $W_c \leftarrow$ collection $c$'s private write-set \\
\quad\quad\quad \textit{// Blocking phase: wait for $n_{required}$ ACKs before responding} \\
\quad\quad\quad $P_{req} \leftarrow \text{SelectAuthorizedPeers}(c.\mathcal{M}, c.n_{required})$ \\
\quad\quad\quad Push $(tx.id, c.id, W_c)$ to all $p_i \in P_{req}$ \\
\quad\quad\quad Wait until $|\{\text{org}(p_i) : p_i \text{ ACKed}\}| \geq c.n_{required}$, or timeout \\
\quad\quad\quad \textbf{if} timeout \textbf{then} return dissemination failure to client \\
\quad 3. Return signed endorsement response to client \\
\quad 4. \textbf{for each} collection $c$ in $tx$'s private write-sets \textbf{do} \\
\quad\quad\quad \textit{// Background phase: spread to remaining peers up to $n_{dissem}$} \\
\quad\quad\quad $P_{dissem} \leftarrow \text{SelectAuthorizedPeers}(c.\mathcal{M}, c.n_{dissem})$ \\
\quad\quad\quad\quad\quad $\setminus\ P_{req}$ \\
\quad\quad\quad Push $(tx.id, c.id, W_c)$ to all $p_i \in P_{dissem}$ (non-blocking) \\[3pt]
\textbf{At Receiving Peer} $p_i$: \\
\quad 1. Verify sender $e$ is authorized for collection $c$ \\
\quad 2. Verify ledger height of $tx$ is within acceptable range \\
\quad 3. Store $(tx.id, c.id, W_c)$ in local transient store \\
\quad 4. Send ACK to endorser $e$ \\
\hline
\end{tabular}
\caption{Proactive dissemination protocol.}
\label{alg:dissemination}
\end{algorithm}
