Prior to the commit of a block, each peer analyzes the transactions and determines if it is missing authorized private data. For each valid transaction, the peer checks every collection referenced in the hashed write-set: if the peer's organization is a member of the collection and the corresponding private write-set is not already present in the local transient store, the collection is marked as missing.

The retrieval process, described in Algorithm~\ref{alg:retrieval}, employs a prioritized pull strategy. When a peer identifies missing data, it constructs a digest for each missing entry---identified by the tuple (transaction ID, namespace, collection, block number, transaction index)---and first attempts to fetch the full collection-level private write-set from the peers that endorsed the transaction, as they are guaranteed to have possessed the data during simulation. If those nodes are unreachable, the requester broadcasts requests to other authorized collection members via the gossip network. Upon receiving a response containing the private write-set, the requester validates it by hashing the data and comparing the result to the hash recorded in the block, ensuring data integrity even when fetching from potentially untrusted neighbors. Retrieval attempts use a fixed-interval retry bounded by a configurable time threshold to avoid overwhelming the network during periods of high congestion. If retrieval still fails after the retry threshold, the peer records the entries as \\textit{eligible missing data} and proceeds with the block commit; a background reconciliation service periodically retries fetching these entries using the same protocol, ensuring eventual data availability without blocking the commit pipeline.

Note that if a smart contract attempts to read private data that is missing from the peer's local store (e.g., due to incomplete dissemination or reconciliation), the \\texttt{GetPrivateData} API returns an error, causing the simulation to fail. This fail-fast behavior prevents the endorser from producing a read-write set based on incomplete state, ensuring that only fully informed simulations contribute to transaction endorsements.

\begin{algorithm}[h]
\centering
\small
\begin{tabular}{|p{0.92\columnwidth}|}
\hline
\textbf{Reactive Retrieval Protocol} \\
\hline
\textbf{Input:} Block $B$ with hashed write-sets, local transient store \\[3pt]
\textbf{At Committing Peer} $p$ (before commit): \\
\quad 1. \textbf{for each} transaction $tx \in B$ \textbf{do} \\
\quad\quad\quad \textbf{if} $tx$ fails endorsement policy \textbf{then skip} \\
\quad 2. \textbf{for each} collection $c$ referenced in $tx$'s hashed write-set \textbf{do} \\
\quad\quad\quad \textbf{if} $p \in c.\mathcal{M}$ \textbf{and} $c$'s private write-set $\notin$ transient store \\
\quad\quad\quad\quad\quad Add digest $(tx.id, c.ns, c.id, B.num, tx.idx)$ to MissingSet \\
\quad 3. \textbf{if} MissingSet $= \emptyset$ \textbf{then} proceed to commit \\
\quad 4. $E \leftarrow$ endorsers of $tx$ \quad\quad\quad \textit{// priority targets} \\
\quad 5. Send pull request with MissingSet digests to $E$ \\
\quad 6. \textbf{for each} private write-set $W_c$ received \textbf{do} \\
\quad\quad\quad Verify $H(W_c)$ matches on-chain hash \\
\quad\quad\quad \textbf{if} valid \textbf{then} store $W_c$ in transient store \\
\quad 7. \textbf{if} MissingSet $\neq \emptyset$ \textbf{then} \\
\quad\quad\quad Broadcast pull request to gossip network \\
\quad\quad\quad Retry with fixed-interval sleep \\
\quad 8. Proceed to commit (missing data tracked \\
\quad\quad\quad for background reconciliation) \\
\hline
\end{tabular}
\caption{Reactive retrieval protocol executed before the commit phase. Missing private write-sets are identified per collection; endorsers are prioritized as data sources with gossip as a fallback.}
\label{alg:retrieval}
\end{algorithm}
