\section{Motivation for Data Privacy}
\label{motivation}
Real-world blockchain deployments span diverse domains---supply chains, healthcare, trade finance---where organizations must share data with relevant parties for coordination while protecting it from unauthorized participants and maintaining auditability. The dual requirement---\textit{share with a subset, auditable by all}---is the defining challenge. We illustrate it through food-supply-chain traceability, a domain where the tension between privacy and auditability is especially acute.

\textbf{Food Traceability.}
In 2006, a major \textit{E. coli} outbreak linked to bagged spinach infected 199 people across 26 U.S. states~\cite{ecoil}. Regulators took two weeks to trace the contamination source, during which significant quantities of safe food were wasted~\cite{blockchain-for-business}. A blockchain-based traceability system addresses this with a tamper-evident, shared record---Walmart demonstrated that blockchain could reduce backtrace time from seven days to 2.2 seconds~\cite{7-to-2, walmart-hf}. However, not all data in a food supply chain has the same visibility requirements. Invoices, pricing terms, quantities, and discount schedules are exchanged strictly between a buyer and a seller---they must remain private from other participants, including competitors transacting with the same partners.

\textit{Why private data must still be on-chain.}
Yet these records cannot simply be kept off-chain. When a buyer and seller later dispute the agreed price or delivery terms, the blockchain's immutable record serves as an authoritative witness that neither party can retroactively alter. Beyond conflict resolution, when an outbreak triggers an FDA investigation and companies must disclose shipment records, the regulator---and indeed any consortium member---must be able to verify that the disclosed records are genuine and unaltered, even if they never held the private data. An on-chain cryptographic anchor makes this possible: a regulator can verify a disclosed record against the ledger without the network ever having stored the plaintext---retroactive fabrication becomes impossible.

\textit{Atomicity across public and private state.}
Updating a public shipment record and its private invoice must succeed or fail together---if one commits without the other, the on-chain hash no longer reflects reality and the audit trail becomes untrustworthy. Food standards authorities~\cite{fs, eu-foodsafety, fao-traceability} mandate detailed record-keeping, yet much of it is commercially sensitive. Without native atomicity, relegating private data to an external database forces organizations to maintain a \textit{shadow} coordination layer---replicating data to authorized parties, enforcing access revocation, and reconciling consistency with the on-chain state---all independently of the blockchain, duplicating overhead the blockchain already subsumes. Integrating privacy into the ledger's native state machine is the only way to guarantee atomicity while eliminating this redundant coordination.

\textbf{Privacy as a Participation Prerequisite.}
Beyond regulatory compliance, transparency creates an economic barrier to participation. Consortium members are often competitors, and blockchain's value increases with participation---yet transparency gives organizations a rational incentive to withhold private data or avoid joining altogether. The audit guarantee makes organizations willing to join despite privacy concerns: each member trusts that on-chain evidence protects the integrity of every transaction, even transactions involving private data they cannot see. Privacy is therefore not merely a compliance requirement; it is a prerequisite for consortium formation, and auditability is the trust mechanism that enables it. These requirements motivate the \textit{private data collection} abstraction formalized next.
