\section{Real-World Impact}

Since its introduction in Hyperledger Fabric v1.2, the private data collection mechanism has become the primary privacy primitive in enterprise blockchain deployments spanning food safety, shipping, pharmaceuticals, aerospace, mining, and finance.

\textbf{Food Safety.}
Walmart's blockchain-based traceability system, built on the IBM Food Trust network~\cite{7-to-2, walmart-hf}, reduced the time to trace a food product from farm to store from seven days to 2.2 seconds. The system now tracks over 25 products across categories---produce, meat, dairy, and multi-ingredient goods---with all leafy-green suppliers mandated to participate. PDCs protect supplier-specific pricing and process data: a retailer and its supplier share bilateral contract terms in a private collection while the shared ledger retains a hash-verified provenance trail that any participant---or a regulator investigating a food-safety incident---can audit.

\textbf{Global Shipping.}
GSBN (Global Shipping Business Network)~\cite{gsbn}, a consortium of eight major carriers and terminal operators including COSCO SHIPPING Lines, Hapag-Lloyd, and PSA International, has processed over one million shipments across nodes in China, the U.S., and Singapore, serving more than 10,000 customers. PDCs keep private trade documents---Bills of Lading, letters of credit, customs declarations---confidential between transacting parties, while the shared ledger provides a single source of truth that reduces cargo-release times from days to hours.

\textbf{Pharmaceuticals.}
The MediLedger project~\cite{mediledger-fda, mediledger-hf} unites 24 companies---including Pfizer, Gilead, McKesson, and Walgreens---to track prescription drugs under the U.S. Drug Supply Chain Security Act (DSCSA)~\cite{dscsa}, an approach validated by an FDA pilot program. MediLedger layers zero-knowledge proofs on top of PDCs: bilateral contract terms and verification responses are stored in private collections, while ZKPs allow a downstream buyer to confirm a drug's authenticity without the seller revealing proprietary pricing. This confirms that PDCs can serve as a substrate for layering additional cryptographic guarantees when the threat model demands them.

\textbf{Mining, Aerospace, and Finance.}
In the \$1.8~trillion metals and mining supply chain, MineHub~\cite{minehub} uses PDCs to connect hundreds of companies---miners, trading houses, financiers, and logistics providers---each receiving its own private collection store for bilateral contract data, replacing the channel model that could not scale to dynamic data-sharing relationships. In aerospace, Honeywell's GoDirect Trade marketplace~\cite{honeywell}---which surpassed \$1~million in sales within ten weeks of launch in the \$4~billion used-aircraft-parts market---uses PDCs to isolate transaction data between buyers and sellers while recording part provenance on the shared ledger to combat counterfeits. In financial services, Oracle's Blockchain Platform~\cite{oracle-cbdc} combines PDCs with Pedersen commitments for a wholesale Central Bank Digital Currency solution: bank account numbers are stored solely in the private data of participating organizations while one-way hashes on the shared ledger enable auditor verification without exposing account attributes.

Across these deployments the underlying pattern is the same: PDCs partition sensitive bilateral data---pricing, contracts, account identifiers, trade documents---while preserving a shared, hash-verified audit trail that satisfies regulatory compliance and cross-party verification. The diversity of industries and trust models confirms that the private data collection abstraction generalizes beyond any single domain.
