\section{Related Work}

\textit{Channels and Sub-Networks.}
Hyperledger Fabric's \textit{channels}~\cite{hf} provide data isolation via independent blockchain instances, each with its own ledger and consensus. While effective, channels are coarse-grained: each data-sharing relationship may require a separate channel, leading to operational complexity. Our mechanism provides fine-grained privacy within one channel.

\textit{Private Transactions via Off-Chain Managers.}
Quorum~\cite{Quorum} and Hyperledger Besu~\cite{besu} both implement a hash-on-chain / data-off-chain model using an external transaction manager (Tessera). However, both have static privacy group membership, require all participants to be online, and offer limited interoperability between private and public state within a single transaction. Our mechanism supports dynamic membership with retroactive reconciliation, tolerates offline peers via gossip, and enables atomic cross-state reads and writes. R3 Corda~\cite{corda} eliminates the global ledger entirely, sharing transactions only on a need-to-know basis. This introduces a \textit{backchain resolution} problem~\cite{corda}: to verify an input state, a recipient must walk the chain of prior transactions that produced it, and each step in this chain may involve data from unrelated parties who never consented to its disclosure. The result is that verifying provenance can inadvertently expose historical data to new counterparties. That same architectural choice also precludes network-wide queries and the tamper-evident audit trail that our on-chain hashes provide.

\textit{Cryptographic Privacy.}
Zero-knowledge proof systems provide strong privacy guarantees: Zerocash~\cite{inproceedings} uses zk-SNARKs~\cite{10.5555/2671225.2671275} for fully anonymous payments; Hawk~\cite{7546538} extends this to smart contracts but requires a trusted manager; Zether~\cite{Bnz2019ZetherTP} enables confidential token transfers via ElGamal encryption and range proofs. All incur significant computational cost (seconds per proof), making them unsuitable for high-throughput enterprise workloads. Our work is complementary---MediLedger~\cite{mediledger-fda, mediledger-hf} demonstrates combining PDCs with ZKPs in practice. Confidential Transactions~\cite{maxwell}, based on Pedersen commitments~\cite{10.1007/3-540-46766-1_9}, hide amounts via homomorphic commitments but not sender/receiver identities. CryptoNote~\cite{Saberhagen2013CryptoNoteV2} (Monero) combines ring signatures and stealth addresses for anonymity. These target permissionless cryptocurrency privacy---a different problem from selective access control in permissioned networks.

\textit{TEEs, MPC, and Homomorphic Encryption.}
TEE-based systems such as Ekiden~\cite{ekiden} and CCF~\cite{ccf} execute smart contracts inside hardware enclaves (e.g., Intel SGX), but introduce hardware dependencies and side-channel vulnerabilities. MPC platforms like Enigma~\cite{enigma} enable joint computation over private inputs, but performance overhead led the project to pivot to TEEs. Fully homomorphic encryption~\cite{gentry-fhe} allows computation on encrypted data but incurs $10^4$--$10^6\times$ overhead. Our approach sidesteps these costs: authorized peers process private data in plaintext while the blockchain stores only hashes, requiring no specialized hardware.

\textit{Off-Chain State Anchoring.}
State channels (e.g., Lightning~\cite{lightning}) and rollups (Optimistic~\cite{optimistic-rollups}, ZK~\cite{zk-rollups}) share the architectural pattern of anchoring off-chain state on a base ledger, but address a different problem: scalability in permissionless networks. Both assume a public verification layer---fraud proofs or validity proofs---that any party can challenge, whereas PDCs restrict both data visibility and verification to authorized collection members. The anchoring mechanism also differs: rollups post compressed transaction data or proofs for global verifiability, while PDCs record only hashes and rely on blind validation for serializability, since the goal is privacy rather than throughput scaling.

\textit{Database-Layer Privacy.}
CryptDB~\cite{cryptdb} executes SQL over encrypted data with practical overhead (15--26\%) but progressively leaks information. Differential privacy~\cite{dwork-dp} provides statistical guarantees against individual record disclosure. These complement our work: PDCs control \textit{who} accesses data at the replication layer, while database techniques limit \textit{what} queries reveal.

\textit{Positioning.}
The distinguishing property of our mechanism is that it achieves fine-grained privacy through architecture---selective replication, on-chain hashes, and blind validation---rather than through expensive cryptographic primitives or hardware trust assumptions. Each alternative surveyed above sacrifices at least one desirable property: ledger-level isolation forfeits fine granularity, eliminating the global ledger forfeits a network-wide audit trail, proof-based confidentiality forfeits throughput, and hardware enclaves forfeit deployment flexibility. PDCs avoid these trade-offs by processing private data in plaintext on authorized peers and recording only hashes on the shared ledger, preserving auditability, atomicity, and smart-contract expressiveness simultaneously.
