\section{Threat Model and Security Analysis}
\label{s:threat-model}
Our design assumes a decentralized network of organizations in which some nodes may be faulty or malicious. We characterize the trust assumptions for each entity class and the security implications.

\textit{Peer Nodes.} For \textit{integrity}, every correct peer independently verifies that received private data matches the on-chain hash before accepting it. This local verification makes hash-data integrity (R2) unconditional from the perspective of a correct peer: no pre-image that does not match the committed hash is ever accepted, regardless of how many peers collude. The endorsement policy serves as the trust assumption for \textit{correct execution}---that the smart contract was honestly evaluated and that the committed hash reflects the true computation result. This assumption is not unique to private data: colluding endorsers that satisfy the policy can equally falsify public state by returning fabricated read-write sets, which the ordering service and non-endorsing peers accept at face value. Private data collections therefore introduce no additional trust assumptions beyond what the base protocol already requires. If all endorsing members of a collection collude, they can commit a fraudulent hash while storing the original private data on their own nodes, bypassing local hash verification. This creates a divergence between the on-chain hash and the private data held by collection members. However, the impact is confined to the colluding peers: any correct peer that later joins the collection will reject the mismatching data during reconciliation, and external auditors can detect the inconsistency by requesting the pre-image and verifying it against the ledger. \textit{Confidentiality} is more nuanced. A malicious peer can leak private data it legitimately holds, or refuse to disseminate data to eligible peers; these are inherent limitations of access-control-based privacy, which prevents unauthorized access but cannot constrain how an authorized party uses data it possesses. Confidentiality is therefore bounded by the weakest collection member. Purging offers no stronger assurance: a malicious member can retain private data locally without honoring purge requests, so purge is best-effort rather than a cryptographic guarantee.

\textit{Clients.} Clients may be malicious, submitting inconsistent private data to different endorsers, fabricating simulation results without sufficient endorsements, or flooding the system with orphan write-sets. The hash mechanism neutralizes inconsistent submissions: if a client sends different private data to different endorsers, each endorser computes a different hash and includes it in its signed response; because the endorsement policy requires matching responses from multiple endorsers, the divergent hashes render the endorsements incompatible and the transaction is rejected during validation. Fabricated simulations are similarly neutralized---peers perform endorsement policy validation \textit{before} attempting to pull any missing pre-images, discarding invalid transactions without fetching their data. For write-set flooding, where a client simulates many transactions but never submits them, a retention window $\Delta$ bounds how long orphan entries persist: the transient store automatically purges entries whose simulation height lags the current ledger height by more than $\Delta$ blocks, and receiving peers reject disseminated write-sets outside this window. The same retention window defends against a malicious \textit{peer} flooding fake write-sets to other collection members; such activity is tracked via monitoring metrics that let operators identify and remediate faulty peers.

\textit{Other Considerations.} Only public and hashed read-write sets are submitted to the ordering service, so ordering nodes never see private data payloads; the ordering layer supports both CFT (Raft) and BFT consensus. We assume a partially synchronous network in which partitions are possible but eventually resolve---a partition may delay private data dissemination, but a peer that cannot obtain private data before commit records it as missing and reconciles once connectivity is restored. Private data must be salted by the client before hashing to prevent adversaries from predicting or confirming the underlying data through brute-force hash comparison. The salt must be provided by the client as part of the transient data rather than generated independently by each peer, because all endorsing peers must produce identical hashes to satisfy the endorsement policy. Regarding data lifecycle, purging removes private data from the off-chain store but the on-chain hash is retained on the immutable ledger; this may not fully satisfy regulations such as GDPR that require complete erasure, and we expect peers to be honest in executing purge operations. Finally, private data collections protect payload content but not transaction \textit{metadata}: the hashed read-write sets recorded on the public ledger reference specific collections, and collection membership policies are visible to all network participants, so any peer can infer which organizations are party to a private transaction even without seeing the underlying data. Mitigating this leakage would require techniques such as zero-knowledge set membership proofs~\cite{zk-set-membership} or anonymous credentials~\cite{camenisch-lysyanskaya}, but even these would only hide which organizations participate; the hashed keys in the read-write sets would still reveal access patterns---analogous to confidential transactions that hide transfer amounts but leave the transaction graph visible.
